---
title: "Fluctuation Amplitude Development: Sensitivity Analyses"
author: "Valerie Jill Sydnor"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: journal
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(cifti)
library(ggseg)
library(ggsegExtra)
library(ggsegGlasser)
library(dplyr)
library(stringr)
library(factoextra)
library(matrixStats)
library(scales)
library(Hmisc)
library(tidyr)
extrafont::loadfonts()
source("/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/R/perm.sphere.p.R")
```

Atlas Labels
```{r}
glasser.parcel.labels <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Maps/parcellations/surface/glasser360_regionlist.csv", header = T)
schaefer.parcel.labels <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Maps/parcellations/surface/schaefer400_regionlist.csv", header = T)
```

Sensorimotor-Association Axis
```{r, warning=F, message=F}
#Glasser 360
S.A.axis.cifti <- read_cifti("/cbica/projects/spatiotemp_dev_plasticity/Maps/S-A_ArchetypalAxis/FSLRVertex/SensorimotorAssociation_Axis_parcellated/SensorimotorAssociation.Axis.Glasser360.pscalar.nii") #S-A_ArchetypalAxis repo, vertex-wise axis average ranks
S.A.axis.glasser <- as.data.frame(cbind(rank(S.A.axis.cifti$data), names(S.A.axis.cifti$Parcel)))
colnames(S.A.axis.glasser) <- c("SA.axis.glasser","orig_parcelname")
S.A.axis.glasser <- merge(S.A.axis.glasser, glasser.parcel.labels, by="orig_parcelname", sort = F)
S.A.axis.glasser$SA.axis.glasser <- as.numeric(S.A.axis.glasser$SA.axis.glasser)
rm(S.A.axis.cifti)

#Schaefer 400
S.A.axis.cifti <- read_cifti("/cbica/projects/spatiotemp_dev_plasticity/Maps/S-A_ArchetypalAxis/FSLRVertex/SensorimotorAssociation_Axis_parcellated/SensorimotorAssociation.Axis.Schaefer400.17Networks.pscalar.nii") #S-A_ArchetypalAxis repo, vertex-wise axis average ranks
S.A.axis.schaefer <- as.data.frame(cbind(rank(S.A.axis.cifti$data), names(S.A.axis.cifti$Parcel)))
colnames(S.A.axis.schaefer) <- c("SA.axis.schaefer","orig_parcelname")
S.A.axis.schaefer$label <- schaefer.parcel.labels$label
S.A.axis.schaefer$SA.axis.schaefer <- as.numeric(S.A.axis.schaefer$SA.axis.schaefer)
rm(S.A.axis.cifti)
```

SNR Mask
```{r}
SNR.mask.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Maps/parcellations/surface/SNRmask_glasser360.csv")
SNR.mask.schaefer <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Maps/parcellations/surface/SNRmask_schaefer400.csv")
```

Spin Test Parcel Rotation Matrix
```{r}
permutations.glasser <- readRDS("/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/glasser_sphericalrotations_N10000.rds")
permutations.schaefer <- readRDS("/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/schaefer_sphericalrotations_N10000.rds")
```

GAM Statistics
```{r, warning=F, message=F}
setwd("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/")

files <- list.files(getwd(), pattern='statistics', ignore.case = F, full.names = F, recursive = T) 

for(file in files){
  varname <- gsub(".*/","", file)
  varname <- gsub('.{4}$', '', varname)
  assign(varname, read.csv(file))
  df.list <- list(get(varname), S.A.axis.glasser, SNR.mask.glasser) #dfs to merge
  assign(varname,  Reduce(function(x,y) merge(x,y, all=TRUE, sort=F), df.list))
 
  varname.spin <- paste(varname, "spin", sep=".")
  assign(varname.spin, (rbind(get(varname)[181:360,], get(varname)[1:180,])))

  assign(varname, (get(varname) %>% filter(SNR.mask != 0)))}
```
```{r}
statistics_schaefer <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_age_statistics_schaefer.csv")
df.list <- list(statistics_schaefer, S.A.axis.schaefer, SNR.mask.schaefer) #dfs to merge
statistics_schaefer <- Reduce(function(x,y) merge(x,y, all=TRUE, sort=F), df.list) 

statistics_schaefer.spin <- statistics_schaefer #left hemisphere -> right hemisphere

statistics_schaefer <- statistics_schaefer %>% filter(SNR.mask != 0)
```

# Age-Dependent Changes in Spontaneous Fluctuations Vary Across the Cortex

## Percent of cortical regions showing significant age effects

### *Low motion*

```{r}
(sum(p.adjust(statistics_lowmotion$Anova.age.pvalue, method=c("fdr")) < 0.05))/(nrow(statistics_lowmotion))*100 
```

### *Psychiatry exclusions*

```{r}
(sum(p.adjust(statistics_ltn$Anova.age.pvalue, method=c("fdr")) < 0.05))/(nrow(statistics_ltn))*100
```

### *Vascular control*

```{r}
(sum(p.adjust(statistics_cbf$Anova.age.pvalue, method=c("fdr")) < 0.05))/(nrow(statistics_cbf))*100 
```

### *T2 signal control*

```{r}
(sum(p.adjust(statistics_T2$Anova.age.pvalue, method=c("fdr")) < 0.05))/(nrow(statistics_T2))*100 
```

### *Normalization*

```{r}
(sum(p.adjust(statistics_norm$Anova.age.pvalue, method=c("fdr")) < 0.05))/(nrow(statistics_norm))*100 
```

### *Atlas*

```{r}
(sum(p.adjust(statistics_schaefer$Anova.age.pvalue, method=c("fdr")) < 0.05))/(nrow(statistics_schaefer))*100 
```


## Cortical smooth functions

Regional smooths plot function
```{r}
plot_gam_smooths <- function(smooths.path, smooths.statistics){

#Read in smooth estimate data
  gamsmooths <- read.csv(smooths.path, header = T)
  colnames(gamsmooths) <- c("age", "est", "index" ,"label")
  gamsmooths <- inner_join(gamsmooths, smooths.statistics, by="label", sort = F)
  gamsmooths.lh <- gamsmooths[33401:67200,]
    
#Create across-region age by smooth estimate plot 
  smooth.plot <- ggplot(gamsmooths.lh, aes(age, est, group = index,color= GAM.age.partialR2)) + 
  geom_line(size = .3, alpha = .8) + 
  paletteer::scale_color_paletteer_c("pals::ocean.matter", direction = -1, limits = c((quantile(smooths.statistics$GAM.age.partialR2, probs = seq(0, 1, 0.05))[2]), (quantile(smooths.statistics$GAM.age.partialR2, probs = seq(0, 1, 0.1))[18])), oob = squish) +
  theme_classic() +
  labs(x = "\nAge", y = "Fluctuation Amplitude\n" ) +
  theme(legend.position = "none") +
  theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 4, family = "Arial", color = c("black")), axis.line = element_line(size=.22), axis.ticks = element_line(size=.22)) +
  scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45)) +
  scale_y_continuous(breaks=c(-.2, 0, .2), expand = c(0.0,0.08))
  
  rm(gamsmooths)
  rm(gamsmooths.lh)
  rm(smooths.statistics)
  gc()
    
  return(smooth.plot)
}
```

### *Low motion*

```{r}
plot_gam_smooths(smooths.path = "/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/lowmotion/smooths_lowmotion.csv", smooths.statistics = statistics_lowmotion)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Lowmotion_smooths.jpg", device = "pdf", dpi = 500, width = 1.85 , height = 1.65)
```

### *Psychiatry exclusions*

```{r}
plot_gam_smooths(smooths.path = "/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/ltn/smooths_ltn.csv", smooths.statistics = statistics_ltn)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Psychiatry_smooths.jpg", device = "pdf", dpi = 500, width = 1.85 , height = 1.65)
```

### *Vascular control*

```{r}
plot_gam_smooths(smooths.path = "/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/cbf/smooths_cbf.csv", smooths.statistics = statistics_cbf)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Vascularcontrol_smooths.jpg", device = "pdf", dpi = 500, width = 1.85 , height = 1.65)
```

### *T2 signal control*

```{r}
plot_gam_smooths(smooths.path = "/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/T2star/smooths_T2.csv", smooths.statistics = statistics_T2)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/T2signalcontrol_smooths.jpg", device = "pdf", dpi = 500, width = 1.85 , height = 1.65)
```

### *Normalization*

```{r}
plot_gam_smooths(smooths.path = "/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/norm//smooths_norm.csv", smooths.statistics = statistics_norm)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Normalization_smooths.jpg", device = "pdf", dpi = 500, width = 1.85 , height = 1.65)
```

### *Atlas*

```{r}
gamsmooths <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_age_smoothestimates_schaefer.csv")
gamsmooths <- inner_join(gamsmooths, statistics_schaefer, by="label", sort = F)
gamsmooths.lh <- gamsmooths[1:37600,]
    
smooth.plot <- ggplot(gamsmooths.lh,aes(age,est,group=index,color=GAM.age.partialR2)) + 
  geom_line(size = .3, alpha = .8) + 
  paletteer::scale_color_paletteer_c("pals::ocean.matter", direction = -1, limits = c((quantile(statistics_schaefer$GAM.age.partialR2, probs = seq(0, 1, 0.05))[2]), (quantile(statistics_schaefer$GAM.age.partialR2, probs = seq(0, 1, 0.1))[18])), oob = squish) +
  theme_classic() +
  labs(x = "\nAge", y = "Fluctuation Amplitude (zero centered)\n" ) +
  theme(legend.position = "none") +
  theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 4, family = "Arial", color = c("black")), axis.line = element_line(size=.22), axis.ticks = element_line(size=.22)) +
  scale_x_continuous(breaks = c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45)) +
  scale_y_continuous(breaks = c(-.2, 0, .2), expand = c(0.0, 0.08))

smooth.plot

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Schaefer_smooths.jpg", device = "pdf", dpi = 500, width = 1.85 , height = 1.65)
```

```{r include=FALSE}
rm(gamsmooths)
rm(gamsmooths.lh)
gc()
```  

# Fluctuation Amplitude Development Unfolds along the Hierarchical Sensorimotor-Association Axis

## Age effects along the S-A Axis

### *Low motion*

```{r}
cor.test(statistics_lowmotion$GAM.age.partialR2, statistics_lowmotion$SA.axis.glasser, method=c("spearman"))

statistics_lowmotion.spin$GAM.age.partialR2[statistics_lowmotion.spin$SNR.mask == 0] <- NA
perm.sphere.p(statistics_lowmotion.spin$GAM.age.partialR2, statistics_lowmotion.spin$SA.axis.glasser, permutations.glasser, corr.type='spearman')
```

### *Psychiatry exclusions*

```{r}
cor.test(statistics_ltn$GAM.age.partialR2, statistics_ltn$SA.axis.glasser, method=c("spearman"))

statistics_ltn.spin$GAM.age.partialR2[statistics_ltn.spin$SNR.mask == 0] <- NA
perm.sphere.p(statistics_ltn.spin$GAM.age.partialR2, statistics_ltn.spin$SA.axis.glasser, permutations.glasser, corr.type='spearman')
```

### *Vascular control*

```{r}
cor.test(statistics_cbf$GAM.age.partialR2, statistics_cbf$SA.axis.glasser, method=c("spearman"))

statistics_cbf.spin$GAM.age.partialR2[statistics_cbf.spin$SNR.mask == 0] <- NA
perm.sphere.p(statistics_cbf.spin$GAM.age.partialR2, statistics_cbf.spin$SA.axis.glasser, permutations.glasser, corr.type='spearman')
```

### *T2 signal control*

```{r}
cor.test(statistics_T2$GAM.age.partialR2, statistics_T2$SA.axis.glasser, method=c("spearman"))

statistics_T2.spin$GAM.age.partialR2[statistics_T2.spin$SNR.mask == 0] <- NA
perm.sphere.p(statistics_T2.spin$GAM.age.partialR2, statistics_T2.spin$SA.axis.glasser, permutations.glasser, corr.type='spearman')
```

### *Normalization*

```{r}
cor.test(statistics_norm$GAM.age.partialR2, statistics_norm$SA.axis.glasser, method=c("spearman"))

statistics_norm.spin$GAM.age.partialR2[statistics_norm.spin$SNR.mask == 0] <- NA
perm.sphere.p(statistics_norm.spin$GAM.age.partialR2, statistics_norm.spin$SA.axis.glasser, permutations.glasser, corr.type='spearman')
```

### *Atlas*

```{r}
cor.test(statistics_schaefer$GAM.age.partialR2, statistics_schaefer$SA.axis.schaefer, method=c("spearman"))

statistics_schaefer.spin$GAM.age.partialR2[statistics_schaefer.spin$SNR.mask == 0] <- NA
perm.sphere.p(statistics_schaefer.spin$GAM.age.partialR2, statistics_schaefer.spin$SA.axis.schaefer, permutations.schaefer, corr.type='spearman')
```

```{r include=FALSE}
rm(list = ls()[grep("statistics", ls())])
gc()
```

# The Neurodevelopmental Hierarchy is Dominant through Adolescence

## Age-specific correlation between derivates and the S-A Axis

```{r}
gam.derivatives.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_age_derivatives_glasser.csv")
```

Derivation-Axis correlation plot function
```{r}
plot_axis_correlation <- function(derivcorrs.path, return_plot = TRUE){

#Read in derivative correlations
  deriv.SAaxis.posteriorcorrs <- read.table(derivcorrs.path, header = F, sep = ",")
  colnames(deriv.SAaxis.posteriorcorrs) <- sprintf("draw%s",seq(from = 1, to = ncol(deriv.SAaxis.posteriorcorrs)))
  deriv.SAaxis.posteriorcorrs <- cbind(deriv.SAaxis.posteriorcorrs, (gam.derivatives.glasser %>% group_by(age) %>% group_keys()))
  
#Age of maximal sensorimotor-association axis correlation: posterior median value + 95% credible interval
  age.max.corr <- deriv.SAaxis.posteriorcorrs %>% #find the age at which the correlation is largest for each draw
    summarise(across(contains("draw"),
                     .fns = function(x){
                       round(deriv.SAaxis.posteriorcorrs$age[which.max(x)],4)
                     }))
  age.max.corr <- t(age.max.corr)
  age.max.corr.median <- median(age.max.corr) #median age #bayes
  age.max.corr.CI <- quantile(age.max.corr, probs = c(0.025, 0.975)) #compute the credible interval based on all draws
  age.max.corr.lower <- age.max.corr.CI[[1]]
  age.max.corr.upper <- age.max.corr.CI[[2]]

#Sensorimotor-association axis correlation value at each age: posterior median values + 95% credible interval
  deriv.SAaxis.posteriorcorrs <- deriv.SAaxis.posteriorcorrs %>% select(contains("draw"))

  deriv.SAaxis.mediancorr <- apply(deriv.SAaxis.posteriorcorrs, 1, function(x){median(x)}) #median correlation value at each age

  cor.credible.intervals <- apply(deriv.SAaxis.posteriorcorrs, 1, function(x){quantile(x, probs = c(0.025, 0.975))}) #compute the credible interval for the correlation value at each age based on all draws
  cor.credible.intervals <- t(cor.credible.intervals)
  cor.credible.intervals <- as.data.frame(cor.credible.intervals)
  cor.credible.intervals <- cbind(cor.credible.intervals, (gam.derivatives.glasser %>% group_by(age) %>% group_keys()))
  cor.credible.intervals$SA.correlation <- deriv.SAaxis.mediancorr 
  colnames(cor.credible.intervals) <- c("lower","upper","age","SA.correlation")
  max.corr.value <- cor.credible.intervals %>% filter(round(age,4) == age.max.corr.median) %>% select(SA.correlation)
  
  cor.credible.intervals$max.corr.CI <- (cor.credible.intervals$age > age.max.corr.lower & cor.credible.intervals$age < age.max.corr.upper) #add a column that indicates whether each age is included in the age of maximal correlation credible interval (T/F)
  cor.credible.intervals$max.cor.window <- cor.credible.intervals$age*cor.credible.intervals$max.corr.CI #add a column that only includes ages in this interval
  cor.credible.intervals$max.cor.window[cor.credible.intervals$max.cor.window == 0] <- NA
                        
  cor.credible.intervals$zero.corr.CI <- (cor.credible.intervals$lower < 0 & cor.credible.intervals$upper > 0) #add a column that indicates whether the credible interval for the correlation includes 0
  cor.credible.intervals$zero.corr.window <- cor.credible.intervals$age*cor.credible.intervals$zero.corr.CI #add a column that only includes ages in the zero window
  cor.credible.intervals$zero.corr.window[cor.credible.intervals$zero.corr.window == 0] <- NA
  
  derivative.correlation.plot <- ggplot(cor.credible.intervals, aes(x = age, y = SA.correlation, ymin = lower, ymax = upper)) + 
    geom_line(size = .3) +
    geom_ribbon(alpha = .2, fill = c("grey30")) +
    labs(x="\nAge", y="Developmental Alignment to the Axis\n") +
    geom_ribbon(aes(x = max.cor.window, y = SA.correlation), fill = "#ba275f") +
    theme_classic() + 
    theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 4, family = "Arial", color = c("black")), axis.line = element_line(size =.22), axis.ticks = element_line(size = .22)) +
    scale_y_continuous(breaks = c(0, 0.2 ,0.4, 0.6), limits = c(-.132,.77)) +
    scale_x_continuous(breaks = c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,0))

  
  rm(deriv.SAaxis.posteriorcorrs)
  rm(cor.credible.intervals)
  gc()
  
  if(return_plot == TRUE){
  return(derivative.correlation.plot)}
  
  if(return_plot == FALSE){
  maxcorr <- cbind(age.max.corr.median, max.corr.value)
  return(maxcorr)}
}
```

### *Low motion*

```{r, message=F, warning=F}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/lowmotion/axiscorrelation_lowmotion.csv")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Lowmotion_axiscorrelation.jpg", device = "pdf", dpi = 500, width = 1.78 , height = 1.65)
```

```{r, message=F, warning=F}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/lowmotion/axiscorrelation_lowmotion.csv", return_plot = FALSE)
```

### *Psychiatry exclusions*

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/ltn/axiscorrelation_ltn.csv")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Psychiatry_axiscorrelation.jpg", device = "pdf", dpi = 500, width = 1.78 , height = 1.65)
```

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/ltn/axiscorrelation_ltn.csv", return_plot = FALSE)
```

### *Vascular control*

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/cbf/axiscorrelation_cbf.csv")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Vascularcontrol_axiscorrelation.jpg", device = "pdf", dpi = 500, width = 1.78 , height = 1.65)
```

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/cbf/axiscorrelation_cbf.csv", return_plot = FALSE)
```

### *T2 signal control*

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/T2star/axiscorrelation_T2.csv")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/T2signalcontrol_axiscorrelation.jpg", device = "pdf", dpi = 500, width = 1.78 , height = 1.65)
```

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/T2star/axiscorrelation_T2.csv", return_plot = FALSE)
```

### *Normalization*

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/norm/axiscorrelation_norm.csv")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Normalization_axiscorrelation.jpg", device = "pdf", dpi = 500, width = 1.78 , height = 1.65)
```

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/sensitivity_analyses/norm/axiscorrelation_norm.csv", return_plot = FALSE)
```

### *Atlas*

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/SAaxis_posteriorderivative_correlation_byage_schaefer.csv")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure5/Schaefer_axiscorrelation.jpg", device = "pdf", dpi = 500, width = 1.78 , height = 1.65)
```

```{r}
plot_axis_correlation("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/SAaxis_posteriorderivative_correlation_byage_schaefer.csv", return_plot = FALSE)
```
