---
title: "Fluctuation Amplitude Development Unfolds Hierarchically Along the Sensorimotor-Association Axis"
author: "Valerie Jill Sydnor"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: journal
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(cifti)
library(ggseg)
library(ggsegExtra)
library(ggsegGlasser)
library(dplyr)
library(stringr)
library(factoextra)
library(matrixStats)
library(scales)
library(Hmisc)
library(tidyr)
library(cocor)
extrafont::loadfonts()
source("/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/R/perm.sphere.p.R")
```

Participant Fluctuation Amplitude Data
```{r}
fluctuations.glasser.pnc <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/PNC/glasserfluctuations_demographics_finalsample.csv") #fMRI + demographics, generated with fitGAMs_fluctuationamplitude_age.R
```

Glasser Labels
```{r}
glasser.parcel.labels <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Maps/parcellations/surface/glasser360_regionlist.csv", header = T) #glasser region list
```

Sensorimotor-Association Axis
```{r, warning=F, message=F}
S.A.axis.cifti <- read_cifti("/cbica/projects/spatiotemp_dev_plasticity/Maps/S-A_ArchetypalAxis/FSLRVertex/SensorimotorAssociation_Axis_parcellated/SensorimotorAssociation.Axis.Glasser360.pscalar.nii") #S-A_ArchetypalAxis repo, vertex-wise axis average ranks
S.A.axis <- as.data.frame(cbind(rank(S.A.axis.cifti$data), names(S.A.axis.cifti$Parcel)))
colnames(S.A.axis) <- c("SA.axis","orig_parcelname")
S.A.axis <- merge(S.A.axis, glasser.parcel.labels, by="orig_parcelname", sort = F)
S.A.axis$SA.axis <- as.numeric(S.A.axis$SA.axis)
rm(S.A.axis.cifti)
```

Intracortical Myelination Developmental Data
```{r message=FALSE, warning=FALSE}
myelin.partialR2.cifti <- read_cifti("/cbica/projects/spatiotemp_dev_plasticity/Myelin/hcpd_n628_myelin_sAge_partial_bayes_r2.pscalar.nii") #T1/T2 ratio - age effect size
myelin.maxdev.cifti <- read_cifti("/cbica/projects/spatiotemp_dev_plasticity/Myelin/hcpd_n628_median_posterior_age_of_max_slope_myelination.pscalar.nii") #age of maximal T1/T2 ratio increase
myelin <- as.data.frame(cbind(myelin.partialR2.cifti$data, myelin.maxdev.cifti$data))
colnames(myelin) <- c("myelin.partialR2","myelin.maxdev")
myelin$label <- glasser.parcel.labels$label
rm(myelin.partialR2.cifti)
rm(myelin.maxdev.cifti)
```

SNR Mask
```{r}
SNR.mask <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Maps/parcellations/surface/SNRmask_glasser360.csv")
```

Spin Test Parcel Rotation Matrix
```{r eval=FALSE, include=TRUE}
source("/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/R/rotate.parcellation.R")
source("/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/R/perm.sphere.p.R")
glasser.coords <- read.table("/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/sphere_HCP.txt", header=F) #coordinates of glasser parcel centroids on the freesurfer sphere
perm.id.full <- rotate.parcellation(coord.l = as.matrix(glasser.coords[1:180,]), coord.r = as.matrix(glasser.coords[181:360,]), nrot = 10000) #rotate the glasser parcellation 10,000 times on the freesurfer sphere to generate spatial nulls for spin-based permutation significance testing 
saveRDS(perm.id.full, "/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/glasser_sphericalrotations_N10000.rds")
```
```{r}
perm.id.full <- readRDS("/cbica/projects/spatiotemp_dev_plasticity/software/rotate_parcellation/glasser_sphericalrotations_N10000.rds") #10,000 spatial null spins
```

GAM Results
```{r}
gam.age.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_age_statistics_glasser.csv") #GAM age smooth statistics, generated with fitGAMs_fluctuationamplitude_age.R

#create df.dev with GAM statistics, S-A axis, plasticity measures, and SNR mask
df.list <- list(gam.age.glasser, S.A.axis, myelin, SNR.mask) #dfs to merge
df.dev <- Reduce(function(x,y) merge(x,y, all=TRUE, sort=F), df.list) 
df.dev <- df.dev %>% select(label, orig_parcelname, everything()) #order columns
cols = c(3:15)    
df.dev[,cols] = apply(df.dev[,cols], 2, function(x) as.numeric(as.character(x))) #format numerics

#create df.dev.spin formatted for spatial permutation testing
df.dev.spin <- rbind(df.dev[181:360,], df.dev[1:180,]) #format df as left hemisphere -> right hemisphere for spin tests
df.dev.spin$GAM.age.partialR2[df.dev.spin$SNR.mask == 0] <- NA #format data for spin tests by assigning NA to low SNR parcels, treating them like the medial wall
df.dev.spin$minage.decrease[df.dev.spin$SNR.mask == 0] <- NA 

df.dev <- df.dev %>% filter(SNR.mask != 0) #include only high SNR parcels (N=336) in analyses
df.dev$SA.axis.bin <- as.numeric(cut2(df.dev$SA.axis, g=10)) #divide the S-A axis into 10 ranked bins
```

```{r}
gam.fitted.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_age_predictedfits_glasser.csv") #GAM predicted fits, generated with fitGAMs_fluctuationamplitude_age.R
gam.fitted.glasser <- inner_join(gam.fitted.glasser, df.dev, by="label", sort = F)
```

```{r}
gam.smoothestimates.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_age_smoothestimates_glasser.csv") #GAM smooth estimates, generated with fitGAMs_fluctuationamplitude_age.R
gam.smoothestimates.glasser <- inner_join(gam.smoothestimates.glasser, df.dev, by="label", sort = F)
```

```{r}
gam.derivatives.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_age_derivatives_glasser.csv") #GAM true model age smooth derivatives, generated with fitGAMs_fluctuationamplitude_age.R
gam.derivatives.glasser <- left_join(gam.derivatives.glasser, S.A.axis, by="label", sort = F)
gam.derivatives.glasser <- left_join(gam.derivatives.glasser, SNR.mask, by="label", sort = F)
gam.derivatives.glasser <- gam.derivatives.glasser %>% filter(SNR.mask != 0) 
```

```{r}
gam.sex.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_agebysex_interaction_glasser.csv") #GAM age spline by sex interaction statistics, generated with fitGAMs_fluctuationamplitude_environment.R

#create df.sex with GAM results, S-A axis, and SNR mask
df.list <- list(gam.sex.glasser, S.A.axis, SNR.mask) #dfs to merge
df.sex <- Reduce(function(x,y) merge(x,y, all=TRUE, sort=F), df.list) 
```

```{r}
gam.env.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/fluctuationamplitude_environment_statistics_glasser.csv") #GAM environment statistics, generated with fitGAMs_fluctuationamplitude_environment.R

#create df.env with GAM results, S-A axis, and SNR mask
df.list <- list(gam.env.glasser, S.A.axis, SNR.mask) #dfs to merge
df.env <- Reduce(function(x,y) merge(x,y, all=TRUE, sort=F), df.list) 

#create df.env.spin formatted for spatial permutation testing
df.env.spin <- rbind(df.env[181:360,], df.env[1:180,]) #format df as left hemisphere -> right hemisphere for spin tests
df.env.spin$GAM.env.tvalue[df.env.spin$SNR.mask == 0] <- NA #format data for spin tests by assigning NA to low SNR parcels, treating them like the medial wall
df.env.spin$GAM.env.edu.tvalue[df.env.spin$SNR.mask == 0] <- NA

df.env <- df.env %>% filter(SNR.mask != 0) #include only high SNR parcels (N=336) in analyses
```

# Age-Dependent Changes in Spontaneous Fluctuations Vary Across the Cortex

## Significant age-related changes in fluctuation amplitude

Number of cortical regions showing significant age effects
```{r}
sum(p.adjust(df.dev$Anova.age.pvalue, method=c("fdr")) < 0.05) #FDR-corrected p-values from full (+age) versus reduced (-age) models
```

Percent of cortical regions showing significant age effects
```{r}
(sum(p.adjust(df.dev$Anova.age.pvalue, method=c("fdr")) < 0.05))/(nrow(df.dev))*100 
```

Across-cortex effect size and (mean derivative) direction
```{r warning=FALSE, include=FALSE}
ggseg(.data = df.dev, atlas = "glasser", mapping=aes(fill=GAM.age.partialR2), position = c("stacked")) + 
  theme_void() + 
  labs(fill="") +
  paletteer::scale_fill_paletteer_c("pals::ocean.matter", direction = -1, limits = c(-0.07, .03), oob = squish) +
  theme(legend.text = element_text(family = "Arial", color = c("black")))

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure1/Brainmap_ageeffect.jpg", device = "pdf", dpi = 500, width = 3 , height = 2)
```

## Age spline by sex interactions

Number of cortical regions show significance age*sex interactions 
```{r}
sum(p.adjust(df.sex$GAM.agexsex.pvalue, method=c("fdr")) < 0.05) #FDR-corrected p-values age by sex interaction testing whether the age spline differs between males and females
```


## Cortical smooth functions

```{r}
gam.smoothestimates.glasser.lh <- gam.smoothestimates.glasser[33401:67200,]
ggplot(gam.smoothestimates.glasser.lh,aes(age,est,group=index,color=GAM.age.partialR2)) + 
  geom_line(size=.3, alpha = .8) + 
  paletteer::scale_color_paletteer_c("pals::ocean.matter", direction = -1, limits = c(-0.07, .03), oob = squish) +
  theme_classic() +
  labs(x = "\nAge", y = "Fluctuation Amplitude (zero centered)\n" ) +
  theme(legend.position = "none") +
  theme(axis.text = element_text(size=6, family = "Arial", color = c("black")), axis.title = element_text(size=6, family = "Arial", color = c("black")), axis.line = element_line(size=.22), axis.ticks = element_line(size=.22)) +
  scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45)) 

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure1/Regional_agesmooths.jpg", device = "pdf", dpi = 500, width = 2.55 , height = 2.3)
```

### Region-specific developmental trajectories and derivatives

**Region V1**

```{r warning=FALSE, include=FALSE}
V1.dev <- df.dev %>% filter(label == "rh_R_V1")
ggseg(.data = V1.dev, atlas = "glasser", mapping=aes(fill=GAM.age.partialR2, colour=I("#ED8B65"), size=I(.03)), position = c("stacked"), hemisphere = "right", view = "medial" ) + 
  theme_void() + 
  labs(fill="") +
  paletteer::scale_fill_paletteer_c("pals::ocean.matter", na.value="transparent", direction = -1, limits = c(-0.07, .03), oob = squish) +
  theme(legend.position = "none")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure1/V1_parcel.jpg", device = "pdf", dpi = 500, width = .5 , height = .5)
```

```{r}
V1.smooth <- gam.fitted.glasser %>% filter(label == "rh_R_V1")
V1.derivatives <- gam.derivatives.glasser %>% filter(label == "rh_R_V1")

scatterplot <- ggplot(data = fluctuations.glasser.pnc, aes(x = age, y = rh_R_V1)) +
  geom_point(color="#FBDC9D", size = .3) +
  geom_line(data = V1.smooth, aes(x = age, y = fitted), color="#F8B57B", size = 1) +
  geom_ribbon(data = V1.smooth, aes(x = age, y = fitted,  ymin = lower, ymax = upper) ,alpha = .7, linetype = 0, fill="#F8B87D",) +
  labs(x="\nAge", y="Fluctuation Amplitude\n") +
  theme_classic() +
  theme(
  axis.text = element_text(size=6, family = "Arial", color = c("black")),
  axis.title.x=element_text(size=6, family ="Arial", color = c("black")),
  axis.title.y=element_text(size=6, family ="Arial", color = c("black")),
  axis.line = element_line(size=.22), axis.ticks = element_line(size=.22)) +
  scale_x_continuous(breaks=c(8, 12, 16, 20), expand = c(0,.45)) +
  scale_y_continuous(breaks=c(1.0, 2.0), labels = c(sprintf("%.1f", round(1, 2)), sprintf("%.1f", round(2, 2))))

derivplot <- ggplot(data = V1.derivatives) + 
  geom_tile(aes(x = age, y = .1, fill = significant.derivative)) +
  scale_fill_gradient(low = "#EFAF77", high = "#FFE0A1", limits = c(-0.0323371,-.01), na.value = "white") +
  labs(x="\nAge", fill = "Derivative") + 
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank(),
          axis.text = element_blank(),
          axis.line = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          legend.text =  element_text(size=6, family = "Arial", color = c("black"))) +
  scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45))

allplots <- list(scatterplot,derivplot)
V1.plot <- cowplot::plot_grid(rel_heights = c(16,3.2), plotlist = allplots, align = "v", axis = "lr", ncol = 1)
V1.plot 

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure1/V1_smooth.jpg", device = "pdf", dpi = 500, width = 2.1 , height = 1.85)
```

**Region p24pr**

```{r warning=FALSE, include=FALSE}
p24pr.dev <- df.dev %>% filter(label == "rh_R_p24pr")
ggseg(.data = p24pr.dev, atlas = "glasser", mapping=aes(fill=GAM.age.partialR2, colour=I("#D54D55"), size=I(.03)), position = c("stacked"), hemisphere = "right", view = "medial" ) + 
  theme_void() + 
  labs(fill="") +
  paletteer::scale_fill_paletteer_c("pals::ocean.matter", na.value="transparent", direction = -1, limits = c(-0.07, .03), oob = squish) +
  theme(legend.position = "none")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure1/p24pr_parcel.jpg", device = "pdf", dpi = 500, width = .5 , height = .5)
```

```{r}
p24pr.smooth <- gam.fitted.glasser %>%filter(label == "rh_R_p24pr")
p24pr.derivatives <- gam.derivatives.glasser %>% filter(label == "rh_R_p24pr")

scatterplot <- ggplot(data = fluctuations.glasser.pnc, aes(x = age, y = rh_R_p24pr)) +
  geom_point(color = "#e06d65", size = .3) +
  geom_line(data = p24pr.smooth, aes(x = age, y = fitted), color="#D54D55", size = 1) +
  geom_ribbon(data = p24pr.smooth, aes(x = age, y = fitted,  ymin = lower, ymax = upper) ,alpha = .7, linetype = 0, fill="#D54D55",) +
  labs(x="\nAge", y="Fluctuation Amplitude\n") +
  theme_classic() +
  theme(
  axis.text = element_text(size=6, family = "Arial", color = c("black")),
  axis.title.x=element_text(size=6, family ="Arial", color = c("black")),
  axis.title.y=element_text(size=6, family ="Arial", color = c("black")),
  axis.line = element_line(size=.22), axis.ticks = element_line(size=.22)) +
  scale_x_continuous(breaks=c(8, 12, 16, 20), expand = c(0,.45)) +
  scale_y_continuous(breaks=c(0.5, 1.0))

derivplot <- ggplot(data = p24pr.derivatives) + 
  geom_tile(aes(x = age, y = .1, fill = significant.derivative)) +
  scale_fill_gradient(high = alpha("#DF5E54",0.7), low = "#D54D55", na.value = "white", limits = c(min(p24pr.derivatives$significant.derivative),-.001)) +
  labs(x="\nAge", fill = "Derivative") + 
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank(),
          axis.text = element_blank(),
          axis.line = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          legend.text =  element_text(size=6, family = "Arial", color = c("black"))) +
  scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45))

allplots <- list(scatterplot,derivplot)
p24pr.plot <- cowplot::plot_grid(rel_heights = c(16,3.2), plotlist = allplots, align = "v", axis = "lr", ncol = 1)
p24pr.plot 

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure1/p24pr_smooth.jpg", device = "pdf", dpi = 500, width = 2.1 , height = 1.85)  
```

**Region IFSa**

```{r warning=FALSE, include=FALSE}
IFSa.dev <- df.dev %>% filter(label == "lh_L_IFSa")
ggseg(.data = IFSa.dev, atlas = "glasser", mapping=aes(fill=GAM.age.partialR2, colour=I("#381043"), size=I(.03)), position = c("stacked"), hemisphere = "left", view = "lateral" ) + 
  theme_void() + 
  labs(fill="") +
  paletteer::scale_fill_paletteer_c("pals::ocean.matter", na.value="transparent", direction = -1, limits = c(-0.07, .03), oob = squish) +
  theme(legend.position = "none")

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure1/IFSa_parcel.jpg", device = "pdf", dpi = 500, width = .5 , height = .5)
```

```{r}
IFSa.smooth <- gam.fitted.glasser %>%filter(label == "lh_L_IFSa")
IFSa.derivatives <- gam.derivatives.glasser %>% filter(label == "lh_L_IFSa")

scatterplot <- ggplot(data = fluctuations.glasser.pnc, aes(x = age, y = lh_L_IFSa)) +
  geom_point(color="#893774", size = .3) +
  geom_line(data = IFSa.smooth, aes(x = age, y = fitted), color="#381043", size = 1) +
  geom_ribbon(data = IFSa.smooth, aes(x = age, y = fitted,  ymin = lower, ymax = upper) ,alpha = .7, linetype = 0, fill="#381043",) +
  labs(x="\nAge", y="Fluctuation Amplitude\n") +
  theme_classic() +
  theme(
  axis.text = element_text(size=6, family = "Arial", color = c("black")),
  axis.title.x=element_text(size=6, family ="Arial", color = c("black")),
  axis.title.y=element_text(size=6, family ="Arial", color = c("black")),
  axis.line = element_line(size=.22), axis.ticks = element_line(size=.22)) +
  scale_x_continuous(breaks=c(8, 12, 16, 20), expand = c(0,.45)) +
  scale_y_continuous(breaks=c(1.0, 2.0), labels = c(sprintf("%.1f", round(1, 2)), sprintf("%.1f", round(2, 2))))

derivplot <- ggplot(data = IFSa.derivatives) + 
  geom_tile(aes(x = age, y = .1, fill = significant.derivative)) +
  scale_fill_gradient2(high = "#6E195E", low = "#cf93c4", midpoint = 0, mid = "white", na.value = "white") +
  labs(x="\nAge", fill = "Derivative") + 
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank(),
          axis.text = element_blank(),
          axis.line = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          legend.text =  element_text(size=6, family = "Arial", color = c("black"))) +
  scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45))

allplots <- list(scatterplot,derivplot)
IFSa.plot <- cowplot::plot_grid(rel_heights = c(16,3.2), plotlist = allplots, align = "v", axis = "lr", ncol = 1)
IFSa.plot 

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure1/IFSa_smooth.jpg", device = "pdf", dpi = 500, width = 2.1 , height = 1.85)  
  
```

# Spatiotemporal Development of Fluctuation Amplitude Follows Intracortical Myelin Growth  

## Spatial development

Fluctuation amplitude age effects map
```{r, warning=F, message=F}
ggseg(.data = df.dev, atlas = "glasser", mapping=aes(fill=GAM.age.partialR2), position = c("stacked"), hemisphere = c("right")) + 
  theme_void() + 
  labs(fill="") +
  paletteer::scale_fill_paletteer_c("pals::ocean.matter", direction = -1, limits = c(-0.07, .03), oob = squish) +
  theme(legend.text = element_blank())

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure2/Brainmap_function.jpg", device = "pdf", dpi = 500, width = 2.4, height = 1.7)
```

T1/T2 ratio age effects map
```{r}
ggseg(.data = df.dev, atlas = "glasser", mapping=aes(fill=myelin.partialR2), position = c("stacked"), hemisphere = "right") + 
  theme_void() + 
  labs(fill="") +
  paletteer::scale_fill_paletteer_c("pals::ocean.matter", direction = 1, limits = c(0.0,0.3), oob = squish) +
  theme(legend.text = element_blank())

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure2/Brainmap_myelin.jpg", device = "pdf", dpi = 500, width = 2.4, height = 1.7)
```

Correlation (rho + p.spin) between fluctuation amplitude age effects and T1/T2 ratio age effects
```{r}
cor.test(df.dev$GAM.age.partialR2, df.dev$myelin.partialR2, method=c("spearman"))
perm.sphere.p(df.dev.spin$GAM.age.partialR2, df.dev.spin$myelin.partialR2, perm.id.full,corr.type='spearman')
```

Correlation plot
```{r}
ggplot(df.dev, aes(x = myelin.partialR2, y = GAM.age.partialR2, fill = GAM.age.partialR2)) + 
geom_point(aes(color = GAM.age.partialR2), shape = 21, size = 1.5) +
paletteer::scale_color_paletteer_c("pals::ocean.matter", direction = -1, limits = c(-0.07, .03), oob = squish) +
paletteer::scale_fill_paletteer_c("pals::ocean.matter", direction = -1, limits = c(-0.07, .03), oob = squish) +
labs(x="\nMyelin Age Effect", y="Fluctuation Amplitude Age Effect\n") +
geom_smooth(method = 'lm', se = TRUE, fill = alpha(c("gray70"),.7), col = "black", size = .75) +
theme_classic() + 
theme(legend.position = "none") +
theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size = .22), axis.ticks = element_line(size = .22))

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure2/Ageeffects_correlationplot.jpg", device = "pdf", dpi = 500, width = 2.68 , height = 2.175)
```

## Temporal development

Fluctuation amplitude age of decrease onset
```{r, warning=F, message=F}
ggseg(.data = df.dev, atlas = "glasser", mapping = aes(fill = minage.decrease), position = c("stacked"), hemisphere = "right") + 
  theme_void() + 
  labs(fill = "") +
  paletteer::scale_fill_paletteer_c("pals::ocean.matter", direction = -1, limits = c(10, 17.5), oob = squish) +
  theme(legend.text = element_blank())

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure2/Brainmap_function_agedecrease.jpg", device = "pdf", dpi = 500, width = 2.4, height = 1.7)
```

T1/T2 ratio age of maximal increase
```{r}
ggseg(.data = df.dev, atlas = "glasser", mapping = aes(fill = myelin.maxdev), position = c("stacked"), hemisphere = "right") + 
  theme_void() + 
  labs(fill = "") +
  paletteer::scale_fill_paletteer_c("pals::ocean.matter", direction = -1, limits = c(10,17.5), oob = squish) +
  theme(legend.text = element_blank())

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure2/Brainmap_myelin_ageincrease.jpg", device = "pdf", dpi = 500, width = 2.4, height = 1.7)
```

Correlation (rho + p.spin) between fluctuation amplitude age of decrease onset and T1/T2 ratio max age of increase
```{r}
#All regions
cor.test(df.dev$minage.decrease, df.dev$myelin.maxdev, method=c("spearman"))
perm.sphere.p(df.dev.spin$minage.decrease, df.dev.spin$myelin.maxdev, perm.id.full,corr.type='spearman')
#Age of decrease onset > 8.5
late.decrease <- df.dev %>% filter(minage.decrease > 8.5)
cor.test(late.decrease$minage.decrease, late.decrease$myelin.maxdev, method=c("spearman"))
late.decrease.spin <- df.dev.spin
late.decrease.spin$minage.decrease[late.decrease.spin$minage.decrease < 8.5] <- NA
perm.sphere.p(late.decrease.spin$minage.decrease, late.decrease.spin$myelin.maxdev, perm.id.full,corr.type='spearman')
```

Correlation plot
```{r, message=F, warning=F}
ggplot(late.decrease, aes(x = myelin.maxdev, y = minage.decrease, fill = minage.decrease)) + 
geom_point(aes(color = minage.decrease), shape = 21, size = 1.2) +
paletteer::scale_fill_paletteer_c("pals::ocean.matter", direction = -1, limits = c(10, 17.5), oob = squish) +
paletteer::scale_color_paletteer_c("pals::ocean.matter", direction = -1, limits = c(10, 17.5), oob = squish) +
labs(x="\nMyelin Age Effect", y="Fluctuation Amplitude Age Effect\n") +
geom_smooth(method = 'lm', se = TRUE, fill = alpha(c("gray70"),.7), col = "black", size = .75) +
theme_classic() + 
theme(legend.position = "none") +
theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size = .22), axis.ticks = element_line(size = .22)) +
scale_y_continuous(breaks=c(10, 12, 14, 16, 18, 20))

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure2/Temporaleffects_correlationplot.jpg", device = "pdf", dpi = 500, width = 2.56 , height = 2.175)
```

# Fluctuation Amplitude Development Unfolds along the Hierarchical Sensorimotor-Association Axis

Sensorimotor-association axis
```{r, warning=F, message=F}
ggseg(.data = df.dev, atlas = "glasser", mapping = aes(fill = SA.axis), position = c("stacked"), hemisphere = "right") + 
  theme_void() + 
  labs(fill = "") +
  scale_fill_gradient2(low = "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = 180) +
  theme(legend.text = element_blank())

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure3/SAaxis.jpg", device = "pdf", dpi = 500, width = 3.65, height = 2.95)
```

## Age effects along the S-A Axis

Correlation (rho + p.spin) between fluctuation amplitude age effects and the sensorimotor-association axis
```{r}
cor.test(df.dev$GAM.age.partialR2, df.dev$SA.axis, method=c("spearman"))
perm.sphere.p(df.dev.spin$GAM.age.partialR2, df.dev.spin$SA.axis, perm.id.full,corr.type='spearman')
```

## Temporal change along the S-A Axis

Correlation (rho + p.spin) between fluctuation amplitude age of decrease onset and the sensorimotor-association axis
```{r}
cor.test(df.dev$minage.decrease, df.dev$SA.axis, method=c("spearman"))
perm.sphere.p(df.dev.spin$minage.decrease, df.dev.spin$SA.axis, perm.id.full,corr.type='spearman')
cor.test(late.decrease$minage.decrease, late.decrease$SA.axis, method=c("spearman"))
perm.sphere.p(late.decrease.spin$minage.decrease, late.decrease.spin$SA.axis, perm.id.full,corr.type='spearman')
```

Sensorimotor-association axis binned GAM smooths 
```{r}
gam.smoothestimates.glasser$age <- round(gam.smoothestimates.glasser$age, 3)

meansmooth.bins <- gam.smoothestimates.glasser %>% group_by(age, SA.axis.bin) %>% do(est.mean = mean(.$est)) %>% unnest(cols = c(est.mean)) #calculate the average smooth estimate at each age within each of the 10 S-A axis bins
```

```{r}
ggplot(data = meansmooth.bins, aes(x = age, y = est.mean, group = SA.axis.bin, color = as.factor(SA.axis.bin))) +
  geom_line(size = 1.5) +
  scale_color_manual(values = c("#FFC228", "#FFCA4E", "#FFD16A", "#FFDA89", "#FFE6B0", "#D7BCDA", "#BE93C4", "#9859A4", "#863E95", "#6F1382")) +
  theme_classic() +
  labs(x = "\nAge", y = "Fluctuation Amplitude (zero centered)\n", color = "Sensorimotor-Association \nAxis Percentile Bin") +
  theme(legend.position = c(.585, 0.94), legend.direction = "horizontal", legend.text = element_text(size = 6), legend.key.size = unit(.3, "cm"), legend.title = element_text(size = 6, family = "Arial", color = c("black"))) +
  theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size=.22), axis.ticks = element_line(size = .22)) + scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45))

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure3/SAaxis_bin_smooths.jpg", device = "pdf", dpi = 500, width = 3.34 , height = 2.15)
```

## Principal developmental gradient

Principal component analysis to identify the spatial axis that captures the most variance in regional fluctuation amplitude developmental trajectories 
```{r}
gam.smoothestimates.glasser <- gam.smoothestimates.glasser %>% select(label, age, est)
gam.smoothestimates.long <- gam.smoothestimates.glasser %>% pivot_wider(names_from="label",values_from="est")
gam.smoothestimates.long <- gam.smoothestimates.long %>% select(-age) #ages by regions matrix for PCA

smooths.pca <- prcomp(gam.smoothestimates.long) #PCA
```

Variance explained by PC1
```{r}
summary(smooths.pca)$importance[2,1]
```

Developmental PC1 correlation with the sensorimotor-association axis
```{r}
PC1 <- as.data.frame(smooths.pca$rotation[,1]) #first principal component loadings
PC1$label <- row.names(PC1) 
colnames(PC1) <- c("PC1","label")
PC1$ranked <- rank(PC1$PC1)

cor.test(PC1$PC1, df.dev$SA.axis, method=c("spearman"))
df.dev.spin <- left_join(df.dev.spin, PC1, by="label")
perm.sphere.p(df.dev.spin$PC1, df.dev.spin$SA.axis, perm.id.full,corr.type='spearman')
```

Correlation plot
```{r, message=F}
PC1 <- left_join(PC1, S.A.axis, by="label")
ggplot(PC1, aes(x = SA.axis, y = PC1, fill = SA.axis)) + 
geom_point(aes(color = SA.axis), shape = 21, size = 1.2) +
scale_fill_gradient2(low = "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = 180) +
scale_fill_gradient2(low = "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "color", name = NULL, midpoint = 180) +
labs(x="\nSensorimtor-Association Axis Rank", y="Principal Developmental Axis Loading\n") +
geom_smooth(method = 'lm', se = TRUE, fill = alpha(c("gray70"),.7), col = "black", size = .25) +
theme_classic() + 
theme(legend.position = "none") +
theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size = .22), axis.ticks = element_line(size = .22))

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure3/AxisPC1_correlationplot.jpg", device = "pdf", dpi = 500, width = 3.34 , height = 2.15)
```

Principal developmental axis brain map 
```{r}
ggseg(.data = PC1, atlas = "glasser", mapping=aes(fill = PC1), position = c("stacked"), hemisphere = "right") + 
theme_void() + 
labs(fill = "") +
scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = -0.05, limits = c(-0.11,0.008), oob = squish) + theme(legend.text = element_blank())

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure3/PC1.jpg", device = "pdf", dpi = 500, width = 3.65, height = 2.95)
```

Developmental PC1 correlation with anatomical, functional, and evolutionary cortical hierarchies
```{r}
maps <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Maps/S-A_ArchetypalAxis/Glasser360_MMP_WholeBrain/brainmaps_glasser.csv")
maps$label <- glasser.parcel.labels$label
df.dev.spin <- left_join(df.dev.spin, maps, by="label")
maps <- merge(PC1, maps, by = "label")
maps <- merge(maps, S.A.axis, by = "label")
```

*Anatomical hierarchy*
```{r}
cor.test(maps$PC1, maps$T1T2ratio, method = c("spearman"))
perm.sphere.p(df.dev.spin$PC1, df.dev.spin$T1T2ratio, perm.id.full, corr.type='spearman')
cocor.dep.groups.overlap(
  r.jk = (cor.test(PC1$PC1, df.dev$SA.axis, method=c("spearman"))$estimate), 
  r.jh = (abs(cor.test(maps$PC1, maps$T1T2ratio, method=c("spearman"))$estimate)), 
  r.kh = (abs(cor.test(maps$T1T2ratio, maps$SA.axis, method=c("spearman"))$estimate)), 
  n = 336, alternative = "two.sided", test = "hittner2003")
```

*Functional hierarchy*
```{r}
cor.test(maps$PC1, maps$G1.fMRI, method = c("spearman"))
perm.sphere.p(df.dev.spin$PC1, df.dev.spin$G1.fMRI, perm.id.full, corr.type='spearman')
cocor.dep.groups.overlap(
  r.jk = (cor.test(PC1$PC1, df.dev$SA.axis, method=c("spearman"))$estimate), 
  r.jh = (abs(cor.test(maps$PC1, maps$G1.fMRI, method=c("spearman"))$estimate)), 
  r.kh = (abs(cor.test(maps$G1.fMRI, maps$SA.axis, method=c("spearman"))$estimate)), 
  n = 336, alternative = "two.sided", test = "hittner2003")
```

*Evolutionary hierarchy*
```{r}
cor.test(maps$PC1, maps$Evolution.Expansion, method = c("spearman"))
perm.sphere.p(df.dev.spin$PC1, df.dev.spin$Evolution.Expansion, perm.id.full, corr.type='spearman')
cocor.dep.groups.overlap(
  r.jk = (cor.test(PC1$PC1, df.dev$SA.axis, method=c("spearman"))$estimate), 
  r.jh = (abs(cor.test(maps$PC1, maps$Evolution.Expansion, method=c("spearman"))$estimate)), 
  r.kh = (abs(cor.test(maps$Evolution.Expansion, maps$SA.axis, method=c("spearman"))$estimate)), 
  n = 336, alternative = "two.sided", test = "hittner2003")
```

Developmental PC1 correlation with S-A axis ranks within mesulam cortical zones
```{r}
glasser.assignments.type <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Maps/parcellations/surface/glasser360-mesulam_economo_yeo-assignments.csv")
glasser.assignments.type <- merge(glasser.assignments.type, S.A.axis, by = "label", sort = F)
glasser.assignments.type <- merge(PC1, glasser.assignments.type, by = "label", sort = F)
```

```{r}
mesulam.corr.estimates <- glasser.assignments.type %>%
  group_by(mesulam_assignment) %>%
  do(correlation = cor.test(.$SA.axis, .$PC1, method = c("spearman"))$estimate) %>%
  unnest(cols = c(correlation))
mesulam.corr.pvalues <- glasser.assignments.type %>%
  group_by(mesulam_assignment) %>%
  do(pvalue = cor.test(.$SA.axis, .$PC1, method = c("spearman"))$p.value) %>%
  unnest(cols = c(pvalue))
mesulam <- merge(mesulam.corr.estimates, mesulam.corr.pvalues)
mesulam$p.fdr <- p.adjust(mesulam$pvalue, method = c("fdr"))
mesulam
```

```{r}
idiotypic <- glasser.assignments.type %>% filter(mesulam_assignment == "idiotypic")
summary(idiotypic$SA.axis)
```

```{r}
unimodal <- glasser.assignments.type %>% filter(mesulam_assignment == "unimodal")
summary(unimodal$SA.axis)
```

```{r}
heteromodal <- glasser.assignments.type %>% filter(mesulam_assignment == "heteromodal")
summary(heteromodal$SA.axis)
```

```{r}
paralimbic <- glasser.assignments.type %>% filter(mesulam_assignment == "paralimbic")
summary(paralimbic$SA.axis)
```

# The Neurodevelopmental Hierarchy is Dominant through Adolescence

## Age-specific fluctuation amplitude derivatives

Regional derivative by age plot
```{r}
gam.derivatives.glasser.lh <- gam.derivatives.glasser[33401:67200,]
ggplot(gam.derivatives.glasser.lh,aes(age,derivative,group=index,color=SA.axis)) + 
  geom_line(size=1, alpha = .7) + 
  scale_color_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "color", name = NULL, midpoint = 180) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x = "\nAge", y = "Derivative\n", color = "Sensorimotor-Association Axis Bin") +
  theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size = .22), axis.ticks = element_line(size = .22)) +
  scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45))
```

```{r}
gam.derivatives.glasser$age <- round(gam.derivatives.glasser$age, 5)
```

Age 10 derivative map
```{r, warning=F, message=F, error=F}
age10.derivs <- gam.derivatives.glasser %>% filter(age == 10.03015)

ggseg(.data = age10.derivs, atlas = "glasser", mapping=aes(fill=derivative), position = c("stacked"), hemisphere = "right") + 
  theme_void() + 
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = -0.012, limits = c(-0.025, 0.005), oob = squish)

rm(age10.derivs)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/Age10_derivatives.jpg", device = "pdf", dpi = 500, width = 2.95 , height = 1.95)
```

Age 10 derivative-axis correlation plot
```{r}
ggplot(age10.derivs, aes(x = SA.axis, y = derivative, fill = derivative)) + 
geom_point(aes(color = derivative), shape = 21, size = .1) +
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = -0.012, limits = c(-0.025, 0.005), oob = squish) +
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "color", name = NULL, midpoint = -0.012, limits = c(-0.025, 0.005), oob = squish) +
labs(x="\nSensorimtor-Association Axis Rank", y="Derivative\n") +
geom_smooth(method = 'lm', se = TRUE, fill = alpha(c("gray70"),.7), col = "black", size = .35) +
theme_classic() + 
theme(legend.position = "none") +
theme(axis.text = element_blank(), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size = .15), axis.ticks = element_line(size = .15)) +
scale_y_continuous(limits = c(-.05, .055), oob = squish)


ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/Age10_correlationplot.jpg", device = "pdf", dpi = 500, width = 1.45 , height = 1.25)
```

Age 15 derivative map
```{r, warning=F, message=F, error=F}
age15.derivs <- gam.derivatives.glasser %>% filter(age == 15.02429)

ggseg(.data = age15.derivs, atlas = "glasser", mapping=aes(fill=derivative), position = c("stacked"), hemisphere = "right") + 
  theme_void() + 
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = -0.012, limits = c(-0.025, 0.005), oob = squish) 

rm(age15.derivs)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/Age15_derivatives.jpg", device = "pdf", dpi = 500, width = 2.95 , height = 1.95)
```

Age 15 derivative-axis correlation plot
```{r}
ggplot(age15.derivs, aes(x = SA.axis, y = derivative, fill = derivative)) + 
geom_point(aes(color = derivative), shape = 21, size = .1) +
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = -0.012, limits = c(-0.025, 0.005), oob = squish) +
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "color", name = NULL, midpoint = -0.012, limits = c(-0.025, 0.005), oob = squish) +
labs(x="\nSensorimtor-Association Axis Rank", y="Derivative\n") +
geom_smooth(method = 'lm', se = TRUE, fill = alpha(c("gray70"),.7), col = "black", size = .35) +
theme_classic() + 
theme(legend.position = "none") +
theme(axis.text = element_blank(), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size = .15), axis.ticks = element_line(size = .15)) +
scale_y_continuous(limits = c(-.05, .055), oob = squish)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/Age15_correlationplot.jpg", device = "pdf", dpi = 500, width = 1.45 , height = 1.25)
```

Age 20 derivative map
```{r, warning=F, message=F, error=F}
age20.derivs <- gam.derivatives.glasser %>% filter(age == 20.01843)

ggseg(.data = age20.derivs, atlas = "glasser", mapping=aes(fill=derivative), position = c("stacked"), hemisphere = "right") + 
  theme_void() + 
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = -0.012, limits = c(-0.025,c0.005), oob = squish)

rm(age20.derivs)

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/Age20_derivatives.jpg", device = "pdf", dpi = 500, width = 2.95 , height = 1.95)
```

Age 20 derivative-axis correlation plot
```{r}
ggplot(age20.derivs, aes(x = SA.axis, y = derivative, fill = derivative)) + 
geom_point(aes(color = derivative), shape = 21, size = .1) +
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = -0.012, limits = c(-0.025, 0.005), oob = squish) +
  scale_fill_gradient2(low= "goldenrod1", mid = "white", high = "#6f1282", guide = "colourbar", aesthetics = "color", name = NULL, midpoint = -0.012, limits = c(-0.025, 0.005), oob = squish) +
labs(x="\nSensorimtor-Association Axis Rank", y="Derivative\n") +
geom_smooth(method = 'lm', se = TRUE, fill = alpha(c("gray70"),.7), col = "black", size = .35) +
theme_classic() + 
theme(legend.position = "none") +
theme(axis.text = element_blank(), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size = .15), axis.ticks = element_line(size = .15)) +
scale_y_continuous(limits = c(-.05, .055), oob = squish)
 
ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/Age20_correlationplot.jpg", device = "pdf", dpi = 500, width = 1.45 , height = 1.25)
```

Derivative by sensorimotor-association axis plot

```{r}
derivative.colorbar <- c("#ff7e38", "#f29049", "#ffa25e", "#faab73", "#fabb73", "#ffcd94", "#ffd894", "#ffe6ab", "#ffe6ab", "#fff5de", "#ffffff", "#f79a97", "#f58682", "#EE6E69", "#C95665", "#BB4166", "#B72863", "#941348", "#7d0f65",  "#660c5f", "#4f0e4a")

ggplot(data=gam.derivatives.glasser,aes(x = age, y = SA.axis, group = index)) +
  geom_line(aes(color=derivative), size=1) +
  scale_color_gradientn(colours = derivative.colorbar, limits=c(-0.028, 0.028), oob = squish) +
  theme_classic() +
  ylab("Sensorimotor-Association Axis Rank\n") +
  xlab("\nAge") +
  labs(color="") +
   theme(axis.text = element_text(size = 7, family = "Arial", color = c("black")), axis.title = element_text(size = 7, family = "Arial", color = c("black")), axis.line = element_line(size =.22), axis.ticks = element_line(size = .22), legend.text = element_text(size = 6, family = "Arial", color = c("black"))) +
  scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0,.45))   

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/Derivative_rank_age_plot.pdf", device = "pdf", dpi = 500, width = 3.7 , height = 4.9)

```

## Age-specific correlation between derivates and the S-A Axis

Posterior derivative - sensorimotor-association axis correlations, N=10,000
```{r}
deriv.SAaxis.posteriorcorrs <- read.table("/cbica/projects/spatiotemp_dev_plasticity/FluctuationAmplitude/GAMRESULTS/SAaxis_posteriorderivative_correlation_byage_glasser.csv", header = F, sep = ",") #get the regional derivative-regional axis rank correlation at each age for all draws from the posterior distribution
colnames(deriv.SAaxis.posteriorcorrs) <- sprintf("draw%s",seq(from = 1, to = ncol(deriv.SAaxis.posteriorcorrs)))
deriv.SAaxis.posteriorcorrs <- cbind(deriv.SAaxis.posteriorcorrs, (gam.derivatives.glasser %>% group_by(age) %>% group_keys()))
```

### Age of maximal sensorimotor-association axis correlation: posterior median value + 95% credible interval

```{r}
age.max.corr <- deriv.SAaxis.posteriorcorrs %>% #find the age at which the correlation is largest for each draw
    summarise(across(contains("draw"),
                     .fns = function(x){
                       round(deriv.SAaxis.posteriorcorrs$age[which.max(x)],4)
                     }))
age.max.corr <- t(age.max.corr)
age.max.corr.median <- median(age.max.corr) #median age #bayes
age.max.corr.CI <- quantile(age.max.corr, probs = c(0.025, 0.975)) #compute the credible interval based on all draws
age.max.corr.lower <- age.max.corr.CI[[1]]
age.max.corr.upper <- age.max.corr.CI[[2]]
```

```{r}
age.max.corr.median
```

```{r}
age.max.corr.CI
```

```{r}
age.max.corr <- as.data.frame(age.max.corr)
ggplot(age.max.corr, aes(x = V1)) + 
geom_histogram(bins = 12, fill = "#FFE5B1") + 
geom_vline(xintercept = 15.0243, color = "#ba275f", size = .5) +
labs(x="\nAge", y="Posterior Draw Number\n") +
theme_classic() +
theme(axis.text.x = element_text(size = 6, family = "Arial", color = c("black")), axis.text.y = element_blank(), axis.title = element_blank(), axis.line = element_blank(), axis.ticks = element_blank()) +
scale_x_continuous(breaks=c(14.5, 15, 15.5))   

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/AgeMaxCorr_histogram.pdf", device = "pdf", dpi = 500, width = 1.03 , height = 1.02)
```

### Sensorimotor-association axis correlation value at each age: posterior median values + 95% credible interval

```{r}
deriv.SAaxis.posteriorcorrs <- deriv.SAaxis.posteriorcorrs %>% select(contains("draw"))

deriv.SAaxis.mediancorr <- apply(deriv.SAaxis.posteriorcorrs, 1, function(x){median(x)}) #median correlation value at each age

cor.credible.intervals <- apply(deriv.SAaxis.posteriorcorrs, 1, function(x){quantile(x, probs = c(0.025, 0.975))}) #compute the credible interval for the correlation value at each age based on all draws
cor.credible.intervals <- t(cor.credible.intervals)
cor.credible.intervals <- as.data.frame(cor.credible.intervals)
cor.credible.intervals <- cbind(cor.credible.intervals, (gam.derivatives.glasser %>% group_by(age) %>% group_keys()))
cor.credible.intervals$SA.correlation <- deriv.SAaxis.mediancorr 
colnames(cor.credible.intervals) <- c("lower","upper","age","SA.correlation")
```

### Window of null sensorimotor-association axis correlation

```{r}
cor.credible.intervals$max.corr.CI <- (cor.credible.intervals$age > age.max.corr.lower & cor.credible.intervals$age < age.max.corr.upper) #add a column that indicates whether each age is included in the age of maximal correlation credible interval (T/F)
cor.credible.intervals$max.cor.window <- cor.credible.intervals$age*cor.credible.intervals$max.corr.CI #add a column that only includes ages in this interval
cor.credible.intervals$max.cor.window[cor.credible.intervals$max.cor.window == 0] <- NA
                        
cor.credible.intervals$zero.corr.CI <- (cor.credible.intervals$lower < 0 & cor.credible.intervals$upper > 0) #add a column that indicates whether the credible interval for the correlation includes 0
cor.credible.intervals$zero.corr.window <- cor.credible.intervals$age*cor.credible.intervals$zero.corr.CI #add a column that only includes ages in the zero window
cor.credible.intervals$zero.corr.window[cor.credible.intervals$zero.corr.window == 0] <- NA
```

```{r}
min(cor.credible.intervals$age[cor.credible.intervals$zero.corr.CI == TRUE])
```

```{r}
max(cor.credible.intervals$age[cor.credible.intervals$zero.corr.CI == TRUE])
```

Sensorimotor-association axis development sliding window plot
```{r}
ggplot(cor.credible.intervals, aes(x = age, y = SA.correlation, ymin = lower, ymax = upper)) + 
geom_line(size = .5) +
geom_ribbon(alpha = .2, fill = c("grey30")) +
labs(x="\nAge", y="Developmental Alignment to the Axis\n") +
geom_ribbon(aes(x = max.cor.window, y = SA.correlation), fill = "#ba275f") +
theme_classic() + 
theme(axis.text = element_text(size = 7, family = "Arial", color = c("black")), axis.title = element_text(size = 7, family = "Arial", color = c("black")), axis.line = element_line(size =.22), axis.ticks = element_line(size = .22)) +
scale_x_continuous(breaks=c(8, 10, 12, 14, 16, 18, 20, 22), expand = c(0, .1)) +
scale_y_continuous(breaks=c(0,0.2,0.4,0.6)) 

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure4/Derivative_SAaxis_correlation_plot.pdf", device = "pdf", dpi = 500, width = 3.82 , height = 2.35)
```

# Fluctuation Amplitude Variability is Linked to Variability in the Developmental Environment

## Significant associations between fluctuation amplitude and environmental factors

Number of cortical regions showing significant environment effects

* original model

```{r}
sum(p.adjust(df.env$Anova.env.pvalue, method=c("fdr")) < 0.05) 
```

* controlling for parental education

```{r}
sum(p.adjust(df.env$Anova.env.edu.pvalue, method=c("fdr")) < 0.05)
```

Percent of cortical regions showing significant environment effects

* original model

```{r}
(sum(p.adjust(df.env$Anova.env.pvalue, method=c("fdr")) < 0.05))/(nrow(df.env))*100 
```

* controlling for parental education

```{r}
(sum(p.adjust(df.env$Anova.env.edu.pvalue, method=c("fdr")) < 0.05))/(nrow(df.env))*100 
```

Across-cortex environment effect size and direction
```{r, warning=F, message=F}
ggseg(.data = df.env, atlas = "glasser", mapping=aes(fill=GAM.env.tvalue), position = c("stacked")) + 
  theme_void() + 
  labs(fill="Age Effect") +
  scale_fill_gradient2(low= "#F9AE76", mid = "white", high = "#952162", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = 0, limits=c(-5,5), oob=squish) +
  theme(legend.text = element_text(size = 6, family = "Arial", color = c("black")))

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure6/Brainmap_enveffect.jpg", device = "pdf", dpi = 500, width = 3.05 , height = 2.25)
```

## Correlation between environmental effects and the sensorimotor-association axis

* original model

```{r}
#all regions
cor.test(df.env$GAM.env.tvalue, df.env$SA.axis, method=c("spearman"))
perm.sphere.p(df.env.spin$GAM.env.tvalue, df.env.spin$SA.axis, perm.id.full, corr.type='spearman')
```

```{r}
#significant regions
df.env.spin$GAM.env.tvalue.significant <- df.env.spin$GAM.env.tvalue*(p.adjust(df.env.spin$Anova.env.pvalue, method=c("fdr")) < 0.05)
df.env.spin$GAM.env.tvalue.significant[df.env.spin$GAM.env.tvalue.significant == 0] <- NA

cor.test(df.env.spin$GAM.env.tvalue.significant, df.env.spin$SA.axis, method=c("spearman"))
perm.sphere.p(df.env.spin$GAM.env.tvalue.significant, df.env.spin$SA.axis, perm.id.full, corr.type='spearman')
```

Correlation plot
```{r, message=F}
df.env$significant <- p.adjust(df.env$Anova.env.pvalue, method=c("fdr")) < 0.05

ggplot(df.env, aes(x = SA.axis, y = GAM.env.tvalue, fill = GAM.env.tvalue, color = significant)) + 
geom_point(size = 1.5, stroke = .12, pch = 21) +
scale_fill_gradient2(low= "#F9AE76", mid = "white", high = "#952162", guide = "colourbar", aesthetics = "fill", name = NULL, midpoint = 0, limits = c(-5,5), oob = squish) +
scale_color_manual(values = c("white","black")) +
labs(x="\nSensorimtor-Association Axis Rank", y="Environment Effect\n") +
geom_smooth(method = 'lm', se = TRUE, fill = alpha(c("gray70"),.7), col = "black", size = .5) +
theme_classic() + 
theme(legend.position = "none") +
theme(axis.text = element_text(size = 6, family = "Arial", color = c("black")), axis.title = element_text(size = 6, family = "Arial", color = c("black")), axis.line = element_line(size = .22), axis.ticks = element_line(size = .22)) +
scale_y_continuous(breaks = c(-5, 0, 5))

ggsave(filename = "/cbica/projects/spatiotemp_dev_plasticity/figures/Manuscript_Figures/Neuron/Figure6/AxisEnv_correlationplot.jpg", device = "pdf", dpi = 500, width = 2.5 , height = 1.7)
```

* controlling for parental education

```{r}
#all regions
cor.test(df.env$GAM.env.edu.tvalue, df.env$SA.axis, method=c("spearman"))
perm.sphere.p(df.env.spin$GAM.env.edu.tvalue, df.env.spin$SA.axis, perm.id.full, corr.type='spearman')
```

```{r}
#significant regions
df.env.spin$GAM.env.edu.tvalue.significant <- df.env.spin$GAM.env.edu.tvalue*(p.adjust(df.env.spin$Anova.env.edu.pvalue, method=c("fdr")) < 0.05)
df.env.spin$GAM.env.edu.tvalue.significant[df.env.spin$GAM.env.edu.tvalue.significant == 0] <- NA

cor.test(df.env.spin$GAM.env.edu.tvalue.significant, df.env.spin$SA.axis, method=c("spearman"))
perm.sphere.p(df.env.spin$GAM.env.edu.tvalue.significant, df.env.spin$SA.axis, perm.id.full, corr.type='spearman')
```
